---
title: "ggplot2 boxplots test"
output: pdf
---
```{r}
library(ggplot2)
library(foreign)
library(Hmisc)
library(reshape2)
library(dplyr)
library(tidyr)
file456 <- spss.get("/Users/AbuDavid/school/census/f456/f456ind.por", use.value.labels=TRUE)
```
Begin with data from Public Use File 2014, file f456.
```{r partTwo}
                                        #
subSetInd2014<-dplyr::select(file456, YEARSUR, WPLDIST,INCSAL)
head(subSetInd2014)
summary(subSetInd2014)
                                        names(subSetInd2014)

                                        ggplot(aes(y=INCSAL,
                                                   x=YEARSUR
                                                    ),
                                   data=subSetInd2014)+geom_boxplot()


                                        ```
       Plot is stretched by very few individuals with extremely high incomes.
       
      Remove these to see the normal salaries more clearly.
       ```{r manipulate}
       richRemoved <- subSetInd2014
  # richRemoved[richRemoved$INCSAL > 1200,] #testSyntax
       count(richRemoved[richRemoved$INCSAL > 40000,]) # > $10k USD/month
  # remove the 130 richest, regraph
       richRemoved<-richRemoved[richRemoved$INCSAL<40000,]
       # ggplot(aes(y=INCSAL,x=YEARSUR),
       #       data=richRemoved)+geom_boxplot()
naRemoved <-richRemoved %>% filter(complete.cases(richRemoved))
 # ggplot(aes(y=INCSAL,  x=YEARSUR  ),
 #                                   data=naRemoved)+geom_boxplot()

               ```
    Here we look at the non-wealthy in the entire country, defined as those who make less than 40k NIS /month, approximately $10k USD/month.
    In shekels, their mean income is 7,488. The middle 50% of them have incomes lying between 2,344 and 10,234 NIS/month.
    ```{r byCity}
  haifaData2014<-  naRemoved %>% filter(WPLDIST == "Haifa")
## ggplot(aes(y=INCSAL,
##            x=YEARSUR,
##            col="green"
##                                                     ),
##        data=haifaData)+geom_boxplot()
##   summary(haifaData)

  centerData2014 <-naRemoved %>% filter(WPLDIST == "Center")
  ## ggplot(aes(y=INCSAL,
  ##            x=YEARSUR,
  ##            col="blue"),
  ##        data=centerData)+geom_boxplot()
  ## summary(centerData)

    ```
    When looking at Haifa, the mean income falls by around 500 NIS to 6944,
    50% of incomes are between 2084 and 9448 NIS.  
    Mean income in the Center is around 500 NIS more than the national mean, and more than 1000 NIS more than the Haifa mean, at 8017. 
    50% of the non-wealthy in Center earn between 2582 and 11,000 NIS. The first quartile is 500 NIS above that of Haifa and the third quartile is 1150 NIS about that of Haifa (11,000 vs. 9448).
    Open new dataSet, Household Expenditure Survey 2013, in file f457.
    
    ```{r moreCities}
judeaData2014<-  naRemoved %>% filter(WPLDIST == "Judea / Samaria")
## ggplot(aes(y=INCSAL,
##            x=YEARSUR,
##            col="orange"
##                                                     ),
##        data=judeaData)+geom_boxplot()
  summary(judeaData)
areas <- c("Haifa","Center","Judea / Samaria")
file457 <- spss.get("/Users/AbuDavid/school/census/f457/f457ind.por", use.value.labels=TRUE)
subSetInd2013<-dplyr::select(file457, YEARSUR, WPLDIST,INCSAL)
 richRemoved2013<-subSetInd2013[subSetInd2013$INCSAL<40000,]
naRemoved2013 <-richRemoved2013 %>% filter(complete.cases(richRemoved2013))
judeaData2013<-  naRemoved2013%>% filter(WPLDIST == "Judea / Samaria")
haifaData2013<-  naRemoved2013 %>% filter(WPLDIST == "Haifa")
centerData2013<- naRemoved2013 %>% filter(WPLDIST == "Center")
national2013<-naRemoved2013
summary(national2013)
summary(judeaData2013)
summary(haifaData2013)
summary(centerData2013)
```
```{r}
ggplot(aes(y=INCSAL,
           x=YEARSUR),
  data=judeaData2013)+geom_boxplot()
```
```{r}

ggplot(aes(y=INCSAL,
           x=YEARSUR
                       ),
       data=haifaData2013)+geom_boxplot()

ggplot(aes(y=INCSAL,
           x=YEARSUR
                       ),
       data=centerData2013)+geom_boxplot()
test1 <- head(centerData2013)
test2 <- head(haifaData2013)
test3 <- head(judeaData2013)
test6 <- head(centerData2014)
test4 <- head(haifaData2014)
test5 <- head(judeaData2014)
test <- rbind(test1, test2, test3, test4, test5, test6)

ggplot(aes(y=INCSAL,
           x=YEARSUR,
           col=WPLDIST
                       ),
       data=test)+geom_boxplot()
#
# summary(test$INCSAL)
#
# mean(test1$YEARSUR)
# mean(test6$YEARSUR)
#
# 

 ```
